---
title: "A comparison of Difference in Differences, Synthetic Controls and
Synthetic Difference in Differences via simulated data - Results"
author: "Benjamin Herzberger"
date: "2024-06-14"
output: html_document
---

```{r Setup, warning = FALSE, message = FALSE}
rm(list=ls())
# Load necessary packages
library(tidyverse)
library(ggplot2)
library(reshape2)
library(RColorBrewer)
library(patchwork)

source("Functions.R")
# Set up relative path for working directory
path <- "C:/Users/benny/OneDrive/Studium/Tübingen/DS in B&E/4. Semester SS2024/B520 Research Seminar on Marketing/Code"
```

This document will not contain any literal results or explanations, but is only used
to visualize the findings of both simulation designs. All interpretations and collection
of the results will be part of the final thesis (PDF). 

## 1.0 Effect of sample size on estimates

```{r Effect of sample sizes, warning = FALSE, message = FALSE}
# Load data
estimates_per_N_random <- read.csv("Output/Data/all_estimates_per_N_random.csv") %>%
  select(-X)
estimates_per_N <- read.csv("Output/Data/all_estimates_per_N.csv") %>%
  select(-X)

# Change to long format for boxplots
random_df_melted <- melt(estimates_per_N_random, id.vars = "N", measure.vars = c("did", "sc", "sdid"), 
                  variable.name = "Method", value.name = "Estimate")
df_melted <- melt(estimates_per_N, id.vars = "N", measure.vars = c("did", "sc", "sdid"), 
                  variable.name = "Method", value.name = "Estimate")

# Adjust method names for labeling
random_df_melted$Method <- factor(random_df_melted$Method, levels = c("did", "sc", "sdid"), labels = c("DiD", "SC", "SDiD"))
df_melted$Method <- factor(df_melted$Method, levels = c("did", "sc", "sdid"), labels = c("DiD", "SC", "SDiD"))

# Visualize estimates in separate boxplots (combined would be nice, but is too cluttered)
# Random treatment assignment
random_N_plot <- ggplot(random_df_melted, aes(x = as.factor(N), y = Estimate, fill = Method)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, alpha = 0.8) + 
  geom_hline(yintercept = 1, color = "red", size = 1, alpha = 0.8) + # Treatment effect
  scale_fill_brewer(palette = "Set2") + 
  labs(
    title = "Distribution of estimates per sample size (random)",
    x = "Sample size",
    y = "Estimate",
    fill = "Method"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 20), 
    axis.title = element_text(face = "bold"), 
    legend.position = "right", 
    legend.title = element_text(face = "bold", size = 15), 
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.title.y = element_text(size = 18)
  ) +
  coord_cartesian(ylim = c(min(df_melted$Estimate), max(df_melted$Estimate))) 

# Non-random treatment assignment
non_random_N_plot <- ggplot(df_melted, aes(x = as.factor(N), y = Estimate, fill = Method)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, alpha = 0.8, varwidth = TRUE) + 
  geom_hline(yintercept = 1, color = "red", size = 1, alpha = 0.8) + # Treatment effect
  scale_fill_brewer(palette = "Set2") + 
  labs(
    title = "Distribution of estimates per sample size (non-random)",
    x = "Sample Size",
    y = "Estimate",
    fill = "Method"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 20), 
    axis.title = element_text(face = "bold"), 
    legend.position = "right", 
    legend.title = element_text(face = "bold", size = 15), 
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.title.y = element_text(size = 18)
  ) +
  coord_cartesian(ylim = c(min(df_melted$Estimate), max(df_melted$Estimate))) 

# Save plots to use in paper
ggsave("Output/Plots/Effect_of_sample_size_random.png", random_N_plot, width = 10, height = 6, dpi = 300)
ggsave("Output/Plots/Effect_of_sample_size_non_random.png", non_random_N_plot, width = 10, height = 6, dpi = 300)
```


## 2.0 Effect of number of pre-treatment periods on estimates

```{r Effect of Treatment periods}
# Load data
estimates_per_period_random <- read.csv("Output/Data/all_estimates_per_period_random.csv") %>%
  select(-X)
estimates_per_period <- read.csv("Output/Data/all_estimates_per_period.csv") %>%
  select(-X)

# Change to long format for boxplots
random_period_df_melted <- melt(estimates_per_period_random, id.vars = "Treatment.Period", measure.vars = c("did", "sc", "sdid"), 
                  variable.name = "Method", value.name = "Estimate")
period_df_melted <- melt(estimates_per_period, id.vars = "Treatment.Period", measure.vars = c("did", "sc", "sdid"), 
                  variable.name = "Method", value.name = "Estimate")

# Adjust method names for labeling
random_period_df_melted$Method <- factor(random_period_df_melted$Method, levels = c("did", "sc", "sdid"), labels = c("DiD", "SC", "SDiD"))
period_df_melted$Method <- factor(period_df_melted$Method, levels = c("did", "sc", "sdid"), labels = c("DiD", "SC", "SDiD"))

# Boxplots
# Random treatment assignment
random_period_plot <- ggplot(random_period_df_melted, aes(x = as.factor(Treatment.Period), y = Estimate, fill = Method)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, alpha = 0.8) + 
  geom_hline(yintercept = 1, color = "red", size = 1, alpha = 0.8) + # Treatment effect
  scale_fill_brewer(palette = "Set2") + 
  labs(
    title = "Distribution of estimates per treatment period (random)",
    x = "Treatment period",
    y = "Estimate",
    fill = "Method"
  ) +
  theme_minimal(base_size = 18) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 20), 
    axis.title = element_text(face = "bold"), 
    legend.position = "right", 
    legend.title = element_text(face = "bold", size = 15), 
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.title.y = element_text(size = 18)
  ) +
  coord_cartesian(ylim = c(min(df_melted$Estimate), max(df_melted$Estimate))) 

# Non-random treatment assignment
non_random_period_plot <- ggplot(period_df_melted, aes(x = as.factor(Treatment.Period), y = Estimate, fill = Method)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, alpha = 0.8, varwidth = TRUE) + 
  geom_hline(yintercept = 1, color = "red", size = 1, alpha = 0.8) + # Treatment effect
  scale_fill_brewer(palette = "Set2") + 
  labs(
    title = "Distribution of estimates per treatment period (non-random)",,
    x = "Treatment period",
    y = "Estimate",
    fill = "Method"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 20), 
    axis.title = element_text(face = "bold"), 
    legend.position = "right", 
    legend.title = element_text(face = "bold", size = 15), 
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.title.y = element_text(size = 18)
  ) +
  coord_cartesian(ylim = c(min(df_melted$Estimate), max(df_melted$Estimate))) 

# Save plots to use in paper
ggsave("Output/Plots/Effect_of_treatment_period_random.png", random_period_plot, width = 10, height = 6, dpi = 300)
ggsave("Output/Plots/Effect_of_treatment_period__non_random.png", non_random_period_plot, width = 10, height = 6, dpi = 300)
```


## 3.0 Effect of heterogeneity on estimates

```{r Effect of heterogeneity}
# Load data
estimates_per_heterogeneity_random <- read.csv("Output/Data/all_estimates_per_deviation_random.csv") %>%
  select(-X)
estimates_per_heterogeneity <- read.csv("Output/Data/all_estimates_per_deviation.csv") %>%
  select(-X)

# Add bias column for plotting
estimates_per_heterogeneity_random <- estimates_per_heterogeneity_random %>% mutate(did_error = abs(did - Effect)) %>% 
  mutate(sc_error = abs(sc - Effect)) %>% mutate(sdid_error = abs(sdid - Effect)) 
estimates_per_heterogeneity <- estimates_per_heterogeneity %>% mutate(did_error = abs(did - Effect)) %>%
  mutate(sc_error = abs(sc - Effect)) %>% mutate(sdid_error = abs(sdid - Effect))

# Compute bias per Treated and Heterogeneity
random_biases <- estimates_per_heterogeneity_random %>% group_by(Treated, Heterogeneity) %>%
  summarise(did_bias = mean(abs(did - Effect)), sc_bias = mean(abs(sc - Effect)), sdid_bias = mean(abs(sdid - Effect))) %>%
  pivot_longer(cols = c(did_bias, sc_bias, sdid_bias), names_to = "Method", values_to = "Bias")

non_random_biases <- estimates_per_heterogeneity %>% group_by(Treated, Heterogeneity) %>%
  summarise(did_bias = mean(abs(did - Effect)), sc_bias = mean(abs(sc - Effect)), sdid_bias = mean(abs(sdid - Effect))) %>%
  pivot_longer(cols = c(did_bias, sc_bias, sdid_bias), names_to = "Method", values_to = "Bias")

# Random treatment
random_bias_plot <- ggplot() +
  geom_line(data = random_biases %>% filter(Treated == 5), 
            aes(x = Heterogeneity, y = Bias, color = Method), size = 1) +
  geom_point(data = random_biases %>% filter(Treated == 5), 
             aes(x = Heterogeneity, y = Bias, color = Method, shape = "Treated = 5"), size = 3) +
  geom_line(data = random_biases %>% filter(Treated == 10), 
            aes(x = Heterogeneity, y = Bias, color = Method), size = 1) +
  geom_point(data = random_biases %>% filter(Treated == 10), 
             aes(x = Heterogeneity, y = Bias, color = Method, shape = "Treated = 10"), size = 3) +
  scale_color_brewer(palette = "Set2",
                     labels = c("did_bias" = "DiD", "sc_bias" = "SC", "sdid_bias" = "SDiD")) +
  scale_shape_manual(name = "Treated", values = c("Treated = 5" = 16, "Treated = 10" = 17),
                     labels = c("Treated = 5" = "5% treated", "Treated = 10" = "10% treated")) +
  labs(
    title = "Bias per heterogeneity in random assignment",
    x = "Standard deviation of treatment effect distribution",
    y = "Bias",
    color = "Method"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 20), 
    axis.title = element_text(face = "bold"), 
    legend.position = "right", 
    legend.title = element_text(face = "bold", size = 15), 
    legend.title.align = 0.5,
    legend.text.align = 0.5, 
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.title.y = element_text(size = 18)
  ) 

# Non-random treatment
non_random_bias_plot <- ggplot() +
  geom_line(data = non_random_biases %>% filter(Treated == 5), 
            aes(x = Heterogeneity, y = Bias, color = Method), size = 1) +
  geom_point(data = non_random_biases %>% filter(Treated == 5), 
             aes(x = Heterogeneity, y = Bias, color = Method, shape = "Treated = 5"), size = 3) +
  geom_line(data = non_random_biases %>% filter(Treated == 10), 
            aes(x = Heterogeneity, y = Bias, color = Method), size = 1) +
  geom_point(data = non_random_biases %>% filter(Treated == 10), 
             aes(x = Heterogeneity, y = Bias, color = Method, shape = "Treated = 10"), size = 3) +
  scale_color_brewer(palette = "Set2",
                     labels = c("did_bias" = "DiD", "sc_bias" = "SC", "sdid_bias" = "SDiD")) +
  scale_shape_manual(name = "Treated", values = c("Treated = 5" = 16, "Treated = 10" = 17),
                     labels = c("Treated = 5" = "5% treated", "Treated = 10" = "10% treated")) +
  labs(
    title = "Bias per heterogeneity in non-random assignment",
    x = "Standard deviation of treatment effect distribution",
    y = "Bias",
    color = "Method"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 20), 
    axis.title = element_text(face = "bold"), 
    legend.position = "right", 
    legend.title = element_text(face = "bold", size = 15), 
    legend.title.align = 0.5,
    legend.text.align = 0.5, 
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.title.y = element_text(size = 18)
  ) 

ggsave("Output/Plots/Bias_per_heterogeneity_random.png", random_bias_plot, width = 10, height = 6, dpi = 300)
ggsave("Output/Plots/Bias_per_heterogeneity_non_random.png", non_random_bias_plot, width = 10, height = 6, dpi = 300)
```

## 4.0 Effect of parallel trends violation on estimates

```{r Violation of parallel trends}
# Load data
estimates_per_trend_random <- read.csv("Output/Data/all_estimates_per_post_treated_trend_random.csv") %>%
  select(-X)
estimates_per_trend_non_random <- read.csv("Output/Data/all_estimates_per_treated_trend.csv") %>%
  select(-X)

# Change to long format for boxplots
random_trend_df_melted <- melt(estimates_per_trend_random, id.vars = "Post.Treated.Trend", measure.vars = c("did", "sc", "sdid"), 
                  variable.name = "Method", value.name = "Estimate")
trend_df_melted <- melt(estimates_per_trend_non_random, id.vars = "Post.Treated.Trend", measure.vars = c("did", "sc", "sdid"),
                  variable.name = "Method", value.name = "Estimate")

# Adjust method names for labeling
random_trend_df_melted$Method <- factor(random_trend_df_melted$Method, levels = c("did", "sc", "sdid"), labels = c("DiD", "SC", "SDiD"))
trend_df_melted$Method <- factor(trend_df_melted$Method, levels = c("did", "sc", "sdid"), labels = c("DiD", "SC", "SDiD"))

# Boxplots
# Random treatment assignment
random_trends_plot <- ggplot(random_trend_df_melted, aes(x = as.factor(Post.Treated.Trend), y = Estimate, fill = Method)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, alpha = 0.8) + 
  geom_hline(yintercept = 1, color = "red", size = 1, alpha = 0.8) + # Treatment effect
  scale_fill_brewer(palette = "Set2") + 
  labs(
    title = "Distribution of estimates per parallel trends violation (random)",
    x = "Post-treatment trend of treatment population",
    y = "Estimate",
    fill = "Method"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 20), 
    axis.title = element_text(face = "bold"), 
    legend.position = "right", 
    legend.title = element_text(face = "bold", size = 15), 
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.title.y = element_text(size = 18)
  ) +
  coord_cartesian(ylim = c(min(df_melted$Estimate), max(df_melted$Estimate))) 

# Non-random treatment assignment
non_random_trends_plot <- ggplot(trend_df_melted, aes(x = as.factor(Post.Treated.Trend), y = Estimate, fill = Method)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, alpha = 0.8, varwidth = TRUE) + 
  geom_hline(yintercept = 1, color = "red", size = 1, alpha = 0.8) + # Treatment effect
  scale_fill_brewer(palette = "Set2") + 
  labs(
    title = "Distribution of estimates per parallel trends violation (non-random)",
    x = "Trend of treatment population",
    y = "Estimate",
    fill = "Method"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 20), 
    axis.title = element_text(face = "bold"), 
    legend.position = "right", 
    legend.title = element_text(face = "bold", size = 15), 
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.title.y = element_text(size = 18)
  ) +
  coord_cartesian(ylim = c(min(df_melted$Estimate), max(df_melted$Estimate))) 

# Save plots to use in paper
ggsave("Output/Plots/Effect_of_parallel_trends_violation_random.png", random_trends_plot, width = 10, height = 6, dpi = 300)
ggsave("Output/Plots/Effect_of_non_parallel_trends.png", non_random_trends_plot, width = 10, height = 6, dpi = 300)
```

## 5.0 Computation times

```{r Computation times}
# Load data
computation_times <- read.csv("Output/Data/computation_times_per_N_random.csv") %>%
  select(-X)

# Rearrange just to make sure that colors are uniform across all plots
computation_times <- computation_times %>% select(N, TWFE, SC, SDiD) %>%
  rename(DiD = TWFE)

# Compute mean per N
mean_times <- computation_times %>% group_by(N) %>% summarise_all(mean)

# Pivot to long format
times_melted <- melt(mean_times, id.vars = "N", measure.vars = c("DiD", "SC", "SDiD"), 
                  variable.name = "Method", value.name = "Time")

# Assuming 'df' is your dataframe
times_line_plot <- ggplot(times_melted, aes(x = as.factor(N), y = Time, color = Method, group = Method)) +
  geom_line(size = 1) + 
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Computation time per sample size",
    x = "Sample size",
    y = "Time in seconds",
    color = "Method"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 20), 
    axis.title = element_text(face = "bold"), 
    legend.position = "right", 
    legend.title = element_text(face = "bold"), 
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank() 
  )
ggsave("Output/Plots/Computation_times_per_N_random.png", times_line_plot, width = 10, height = 6, dpi = 300)
mean_times
# Print mean times rounded to 4 digits
round(mean_times, 4)
```


## Really large samples

Since the findings about really large sample sizes are not that interesting, they will
not be included in the final thesis. After being instructed to research this aspect, 
I expected the results to be surprising. However, basically all methods produce similar
results as in settings where fewer observations were regarded. Unfortunately, this took quite
some time, as the computation on the cluster took further steps to enable this analysis.
If the page limit of the thesis was increased, the results would definitely be included, but
since contents of the thesis have to be selected carefully, this part will be omitted. 
It is however remarkable, that SDiD produces identical results in all settings. 

```{r Really large samples}
# Load data
estimates_per_N_large_random <- read.csv("Output/Cluster/Output/Data/all_estimates_large_sample_random.csv") %>%
  select(-X)
estimates_per_N_large_mean <- read.csv("Output/Cluster/Output/Data/all_estimates_large_sample_diff_mean.csv") %>%
  select(-X)
estimates_per_N_large_trend <- read.csv("Output/Cluster/Output/Data/all_estimates_large_sample_diff_trend.csv") %>%
  select(-X)

estimates_per_N_large_random <- melt(estimates_per_N_large_random, id.vars = "N", measure.vars = c("did", "sc", "sdid"), 
                  variable.name = "Method", value.name = "Estimate")
estimates_per_N_large_mean <- melt(estimates_per_N_large_mean, id.vars = "N", measure.vars = c("did", "sc", "sdid"), 
                  variable.name = "Method", value.name = "Estimate")
large_diff_trend_df_melted <- melt(estimates_per_N_large_trend, id.vars = "N", measure.vars = c("did", "sc", "sdid"),
                  variable.name = "Method", value.name = "Estimate")

# Adjust method names for labeling
estimates_per_N_large_random$Method <- factor(estimates_per_N_large_random$Method, levels = c("did", "sc", "sdid"), labels = c("DiD", "SC", "SDiD"))
estimates_per_N_large_mean$Method <- factor(estimates_per_N_large_mean$Method, levels = c("did", "sc", "sdid"), labels = c("DiD", "SC", "SDiD"))
large_diff_trend_df_melted$Method <- factor(large_diff_trend_df_melted$Method, levels = c("did", "sc", "sdid"), labels = c("DiD", "SC", "SDiD"))

# Boxplots
# Random treatment assignment
random_N_large_plot <- ggplot(estimates_per_N_large_random, aes(x = as.factor(N), y = Estimate, fill = Method)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, alpha = 0.8) + 
  geom_hline(yintercept = 1, color = "red", size = 1, alpha = 0.8) + # Treatment effect
  scale_fill_brewer(palette = "Set2") + 
  labs(
    title = "Distribution of estimates per sample size (random)",
    x = "Sample size",
    y = "Estimate",
    fill = "Method"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 20), 
    axis.title = element_text(face = "bold"), 
    legend.position = "right", 
    legend.title = element_text(face = "bold"), 
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank() 
  ) +
  coord_cartesian(ylim = c(min(estimates_per_N_large_random$Estimate), max(estimates_per_N_large_random$Estimate)))

# Diff-mean
diff_mean_N_large_plot <- ggplot(estimates_per_N_large_mean, aes(x = as.factor(N), y = Estimate, fill = Method)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, alpha = 0.8) + 
  geom_hline(yintercept = 1, color = "red", size = 1, alpha = 0.8) + # Treatment effect
  scale_fill_brewer(palette = "Set2") + 
  labs(
    title = "Distribution of estimates per sample size (diff-mean)",
    x = "Sample size",
    y = "Estimate",
    fill = "Method"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 20), 
    axis.title = element_text(face = "bold"), 
    legend.position = "right", 
    legend.title = element_text(face = "bold"), 
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank() 
  ) +
  coord_cartesian(ylim = c(min(estimates_per_N_large_mean$Estimate), max(estimates_per_N_large_mean$Estimate)))

# Diff-trend
diff_trend_N_large_plot <- ggplot(large_diff_trend_df_melted, aes(x = as.factor(N), y = Estimate, fill = Method)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, alpha = 0.8) + 
  geom_hline(yintercept = 1, color = "red", size = 1, alpha = 0.8) + # Treatment effect
  scale_fill_brewer(palette = "Set2") + 
  labs(
    title = "Distribution of estimates per sample size (diff-trend)",
    x = "Sample size",
    y = "Estimate",
    fill = "Method"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 20), 
    axis.title = element_text(face = "bold"), 
    legend.position = "right", 
    legend.title = element_text(face = "bold"), 
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank() 
  ) +
  coord_cartesian(ylim = c(min(large_diff_trend_df_melted$Estimate), max(large_diff_trend_df_melted$Estimate)))
```

## Exemplary visualizations

For one random and one non-random study design: Visualize the development of one single data frame,
visualize the development of all data frames (mean) and visualize estimate distribution.

```{r Exemplary visualizations}
# Set parameters that are used for plotting
treatment_effect <- 1
iterations <- 1000

# For random assignment, the simulation with varying number of pre-treatment
# periods is considered. More specifically, the one in which treatment is applied 
# in period 5 is considered.
N <- 9
n_treated <- 1
treatment_period <- 5
example_df <- read.csv("Output/Data/Example DFs/example_df_treatment_period_5_random.csv")
estimates_random <- read.csv("Output/Data/all_estimates_per_period_random.csv") %>%
  select(-X) %>% filter(Treatment.Period == 5)

# Plot estimate distribution
estimate_plot_random <- plot_estimates(estimates_random)

# Plot individual example
individual_plot_random <- plot_individual(example_df)

# Save plots to use in thesis
ggsave("Output/Plots/Estimate_distribution_random.png", estimate_plot_random, width = 10, height = 6, dpi = 300)
ggsave("Output/Plots/Individual_example_random.png", individual_plot_random, width = 10, height = 6, dpi = 300)

# For non random treatment, the simulation with degree of violation of 
# parallel trends is considered. Further, the configuration in which the treated
# trend is set to 0.5 is considered.
treatment_period <- 8
N <- 100
n_treated <- 5
example_df_non_random <- read.csv("Output/Data/Example DFs/example_df_treated_trend_0.5.csv")
estimates_non_random <- read.csv("Output/Data/all_estimates_per_treated_trend.csv") %>%
  select(-X) %>% filter(Post.Treated.Trend == 0.5)

# Plot estimate distribution
estimate_plot_random <- plot_estimates(estimates_non_random)

# Plot individual example
individual_plot_random <- plot_individual(example_df_non_random)

# Save plots to use in thesis
ggsave("Output/Plots/Estimate_distribution_non_random.png", estimate_plot_random, width = 10, height = 6, dpi = 300)
ggsave("Output/Plots/Individual_example_non_random.png", individual_plot_random, width = 10, height = 6, dpi = 300)
```

