---
title: "A comparison of Difference in Differences, Synthetic Controls and
Synthetic Difference in Differences via simulated data"
author: "Benjamin Herzberger"
date: "2024-06-13"
output: html_document
---

```{r Setup}
rm(list=ls())
source("Functions.R")

# Set up estimators to be used in the estimation via {synthdid} package
estimators = list(did = did_estimate, sc = sc_estimate, sdid = synthdid_estimate)

# Set seed for replicability
set.seed(100)

# Draw random index to select 1 dataframe per simulation for visualization
index <- round(runif(1, 1, 1000)) 

# Set up relative path for working directory
path <- "C:/Users/benny/OneDrive/Studium/Tübingen/DS in B&E/4. Semester SS2024/B520 Research Seminar on Marketing/Code"
```


## 2.0 Non-random treatment assignment 

To recreate non-random treatment assignment, the to be treated population will be modeled
to not evolve in parallel to the control population. Initial values are, in most simulations,
still drawn from the same distribution however. 
In the context of homogeneous treatment effects,the number of treated units will strictly
be set to 1. In the context of heterogeneous treatment effects, the number of treated units
will be set to amount to 5%/10% of the total sample size. 


### 2.1 Effect of sample size on estimates

To test the influence that sample size has on the estimates of all three methods,
we will vary the control population from 5 to 1000 units, while always only treating 1 unit.
All other variables are fixed to isolate the effect of the sample size and enhance
comparability across simulation designs. Each simulation will be carried out 1000 times.
The pre- as well as the post-treatment trend for treated units will be set to be 0.1 larger than the
control groups' trends to emulate non-random treatment assignment. 

```{r Effect of sample sizes}
# Set seed anew, so chunks can also be run independently
set.seed(100)

# Set parameters for simulation
iterations <- 1000
T <- 10
n_treated <- 1
pre_control_trend <- 0.1
pre_treated_trend <- 0.2
post_control_trend <- 0.1
post_treated_trend <- 0.2
treatment_effect <- 1
control_sizes <- c(5, 10, 50, 100, 500, 1000)
treatment_period <- T - 2

# Set treatment effect to be static (only applied once)
effect = "static"

# Initialize df to store estimates per iteration
all_estimates <- data.frame(matrix(ncol = 5, nrow = 0))
colnames(all_estimates) <- c("Effect", "N", "did", "sc", "sdid")


for(i in 1:length(control_sizes)){
  
  # Grab N and n_treated 
  N <- control_sizes[i]
  
  # Set up list of simulation parameters
  simulation_params <- list(N = control_sizes[i], T = T, n_treated = n_treated, treatment_period = treatment_period,
                           pre_control_trend = pre_control_trend, pre_treated_trend = pre_treated_trend,
                           post_control_trend = post_control_trend, post_treated_trend = post_treated_trend,
                           treatment_effect = treatment_effect, effect = effect)
  
  # Simulation & estimation
  results <- repeated_simulation(simulation_function = treatment_simulation,
                                     simulation_params = simulation_params, iterations = iterations)
  # Grab estimates
  estimates <- results$estimates
  
  # Grab one example df at random index
  df <- results$dfs[[index]]
 
  # Save example df
  write.csv(df, paste0(path, "/Output/Data/Example DFs/example_df_N_", N, ".csv"))
  
  # Add additional simulation parameters to estimates
  estimates <- cbind(treatment_effect, N, estimates)
  colnames(estimates) <- c("Effect", "N", "did", "sc", "sdid")
  
  # Append estimates to all_estimates dataframe
  all_estimates <- rbind(all_estimates, estimates)
  
  # Save plot of grouped simulations within each iteration
  plot_grouped_simulations(results$dfs) %>%
    ggsave(filename = paste0(path, "/Output/Plots/data_plot_N_", N, ".png"), width = 10, height = 5, units = "in", dpi = 300)
  
  # Print progress info
  print(paste0("Finished simulation for N = ", N, " and n_treated = ", n_treated, " at ", Sys.time()))
}

# Save all estimates
write.csv(all_estimates, paste0(path, "/Output/Data/all_estimates_per_N.csv"))
```


#### 2.2 Effect of pre-treatment periods on estimates

To test the influence that the number of pre-treatment periods has on the estimates of
all three methods, all variables except the treatment period, and consequently the 
number of pre-treatment periods, will be kept constant. The number of pre-treatment periods
will be varied from 3 (earliest possible treatment) to 10 (last period). 
In order to still highlight one of SDiD's and SC's main advantages, the overall 
sample size is rather small. Each simulation will again be carried out 1000 times. 
Again, the pre- as well as the post-treatment trend for treated units will be set to be 0.1 larger than the
control groups' trends to emulate non-random treatment assignment.

```{r Effect of Treatment periods}
set.seed(100)

# Set addutional simulation parameters
N <- 9

# Setting a lower value than 3 is not possible 
treatment_periods = c(3, 4, 5, 6, 7, 8, 9, 10)

# Initialize df to store estimates per iteration
all_estimates <- data.frame(matrix(ncol = 5, nrow = 0))
colnames(all_estimates) <- c("Effect", "N", "did", "sc", "sdid")

for(i in 1:length(treatment_periods)){
  
  treatment_period <- treatment_periods[i]
  simulation_params <- list(N = N, T = T, n_treated = n_treated, treatment_period = treatment_period,
                           pre_control_trend = pre_control_trend, pre_treated_trend = pre_treated_trend,
                           post_control_trend = post_control_trend, post_treated_trend = post_treated_trend,
                           treatment_effect = treatment_effect, effect = effect)
  
  # Simulation & estimation
  results <- repeated_simulation(simulation_function = treatment_simulation,
                                     simulation_params = simulation_params, iterations = iterations)
  # Grab estimates
  estimates <- results$estimates
  
  # Grab one example df at random index
  df <- results$dfs[[index]]
  
  # Save example df
  write.csv(df, paste0(path, "/Output/Data/Example DFs/example_df_treatment_period_", treatment_period, ".csv"))
  
  # Add additional simulation parameters to estimates
  estimates <- cbind(treatment_effect, treatment_period, estimates)
  colnames(estimates) <- c("Effect", "Treatment Period", "did", "sc", "sdid")
  
  # Append estimates to all_estimates dataframe
  all_estimates <- rbind(all_estimates, estimates)

  # Save plot of grouped simulations within each iteration
  plot_grouped_simulations(results$dfs) %>%
    ggsave(filename = paste0(path, "/Output/Plots/data_plot_treatment_period_",
                             treatment_period, ".png"), width = 10, height = 5, units = "in", dpi = 300)
  # Print progress info
  print(paste0("Finished simulation for treatment period = ", treatment_period, " at ", Sys.time()))
}

# Save all estimates
write.csv(all_estimates, paste0(path, "/Output/Data/all_estimates_per_period.csv"))
```


#### 2.3 Effect of heterogeneity (treatment effect) on estimates

To test the effect that heterogeneous treatment effects have on the three different estimation
methods, the treatment will now be drawn from a Normal distribution with a mean of 
the treatment effect and an increasing standard deviation, which serves as a means to model the
heterogeneity in the treatment effect. The number of treated units will be set to 5%/10% of the
overall population size. However, in order for heterogeneity to "take effect" a sufficient
number of treated units has to be simulated. Slightly larger sample sizes will therefore
be considered in this context. Each simulation will be carried out 1000 times. 
Again, the pre- as well as the post-treatment trend for treated units will be set to be 0.1 larger than the
control groups' trends to emulate non-random treatment assignment.

```{r Effect of heterogeneity}
set.seed(100)

# Set up additional parameters
heterogeneity <- c(1, 2, 3, 4, 5)
treatment_period <- T - 2

# Set overall sample size to 100, to allow for 5% and 10% share of treated units
N <- 100
treated_sizes <- c(5, 10)
combinations <- length(heterogeneity) * length(treated_sizes)

# Initialize df to store estimates per iteration
all_estimates <- data.frame(matrix(ncol = 6, nrow = 0))
colnames(all_estimates) <- c("Effect", "Heterogeneity", "treated", "did", "sc", "sdid")

# Loop over combinations of heterogeneity and treated sizes
for(i in 1:length(treated_sizes)){
  
  n_treated <- treated_sizes[i]
  
    for (j in 1:length(heterogeneity)){
      
      deviation <- heterogeneity[j]
    
      simulation_params <- list(N = N, T = T, n_treated = n_treated, treatment_period = treatment_period,
                           pre_control_trend = pre_control_trend, pre_treated_trend = pre_treated_trend,
                           post_control_trend = post_control_trend, post_treated_trend = post_treated_trend,
                           treatment_effect = treatment_effect, deviation = deviation, effect = effect)
  
      # Simulation & estimation
      results <- repeated_simulation(simulation_function = heterogeneous_treatment_simulation,
                                     simulation_params = simulation_params, iterations = iterations)
      # Grab estimates
      estimates <- results$estimates
  
      # Grab one example df at random index
      df <- results$dfs[[index]]
  
      # Save example df
      write.csv(df, paste0(path, "/Output/Data/Example DFs/example_df_deviation", deviation, ".csv"))
      
      # Add additional simulation parameters to estimates
      estimates <- cbind(treatment_effect, deviation, n_treated, estimates)
      colnames(estimates) <- c("Effect", "Heterogeneity", "Treated", "did", "sc", "sdid")
      
      # Append estimates to all_estimates dataframe
      all_estimates <- rbind(all_estimates, estimates)

      # Save plot of grouped simulations within each iteration
      plot_grouped_simulations(results$dfs) %>%
      ggsave(filename = paste0(path, "/Output/Plots/data_plot_dev_",
                             deviation, "_n_treated_", n_treated, ".png"), width = 10, height = 5, units = "in", dpi = 300)

      # Print progress info
      print(paste0("Finished simulation for deviation = ", deviation, " and n_treated = ", n_treated, " at ", Sys.time()))
  }
}

# Save all estimates
write.csv(all_estimates, paste0(path, "/Output/Data/all_estimates_per_deviation.csv"))
```


### 2.4 Violation of the parallel trends assumption

In contrast to the random simulations, parallel trends will now be violated "differently".
For non-random treatment assignment, trends are set to not be parallel to begin with. However,
the extent to which they are un-parallel will be varied in the following. While the control group will
still exhibit a constant trend of 0.1, the treated group will exhibit trends of 0.2, 0.3, 0.5 and 1.
Choosing a sufficiently large sample size 

```{r Violation of parallel trends}
set.seed(100)

# Set additional parameters
N <- 100
n_treated <- 5
treated_trends <- c(0.2, 0.3, 0.5, 0.75, 1)

# Initialize df to store estimates per iteration
all_estimates <- data.frame(matrix(ncol = 5, nrow = 0))
colnames(all_estimates) <- c("Effect", "Post Treated Trend", "did", "sc", "sdid")

for(i in 1:length(post_treated_trends)){
  
  pre_treated_trend <- treated_trends[i]
  post_treated_trend <- pre_treated_trend
  
  simulation_params <- list(N = N, T = T, n_treated = n_treated, treatment_period = treatment_period,
                           pre_control_trend = pre_control_trend, pre_treated_trend = pre_treated_trend,
                           post_control_trend = post_control_trend, post_treated_trend = post_treated_trend,
                           treatment_effect = treatment_effect, effect = effect)
  
  # Simulation & estimation
  results <- repeated_simulation(simulation_function = treatment_simulation,
                                     simulation_params = simulation_params, iterations = iterations)
  # Grab estimates
  estimates <- results$estimates
  
  # Grab one example df at random index
  df <- results$dfs[[index]]
  
  # Save example df
  write.csv(df, paste0(path, "/Output/Data/Example DFs/example_df_treated_trend_", pre_treated_trend, ".csv"))
  
  # Add additional simulation parameters to estimates
  estimates <- cbind(treatment_effect, post_treated_trend, estimates)
  colnames(estimates) <- c("Effect", "Post Treated Trend", "did", "sc", "sdid")
  
  # Append estimates to all_estimates dataframe
  all_estimates <- rbind(all_estimates, estimates)
  
  # Save plot of grouped simulations within each iteration
  plot_grouped_simulations(results$dfs) %>%
    ggsave(filename = paste0(path, "/Output/Plots/data_plot_treated_trend_",
                             post_treated_trend, ".png"), width = 10, height = 5, units = "in", dpi = 300)
  
  # Print progress info
  print(paste0("Finished simulation for treated trend = ", pre_treated_trend, " at ", Sys.time()))
}

# Save all estimates
write.csv(all_estimates, paste0(path, "/Output/Data/all_estimates_per_treated_trend.csv"))
```



