---
title: "A comparison of Difference in Differences, Synthetic Controls and
Synthetic Difference in Differences via simulated data"
author: "Benjamin Herzberger"
date: "2024-06-13"
output: html_document
---

```{r Setup, warning = FALSE, message = FALSE}
rm(list=ls())
source("Functions.R")

# Set up estimators to be used in the estimation via {synthdid} package
estimators = list(did = did_estimate, sc = sc_estimate, sdid = synthdid_estimate)

# Set seed for replicability
set.seed(100)

# Draw random index to select 1 dataframe per simulation for visualization
index <- round(runif(1, 1, 1000)) 

# Set up relative path for working directory
path <- "C:/Users/benny/OneDrive/Studium/Tübingen/DS in B&E/4. Semester SS2024/B520 Research Seminar on Marketing/Code"
```


## 1.0 Random treatment assignment 

To recreate random treatment assignment, both populations will be modeled to be very similar:
Initial values are drawn from the same Normal distribution and pre-/ as well as post-treatment
trends are the same for both groups. In the context of homogeneous treatment effects,
the number of treated units will strictly be set to 1. In the context of heterogeneous
treatment effects, the number of treated units will be set to amount to 5%/10% of the
total sample size. 


### 1.1 Effect of sample size on estimates

To test the influence that sample size has on the estimates of all three methods,
in the static treatment effect setting, we will vary the control population from 
5 to 1000 units, while always only treating 1 unit. All other variables are fixed
to isolate the effect of the sample size and enhance comparability across simulation
designs. Each simulation will be carried out 1000 times.

```{r Effect of sample sizes}
# Set seed anew, so chunks can also be run independently
set.seed(100)

# Set parameters for simulation
iterations <- 1000
T <- 10
n_treated <- 1
pre_control_trend <- 0.1
pre_treated_trend <- pre_control_trend
post_control_trend <- pre_control_trend
post_treated_trend <- pre_control_trend
treatment_effect <- 1
control_sizes <- c(5, 10, 50, 100, 500, 1000)
treatment_period <- T - 2

# Set treatment effect to be static (only applied once)
effect = "static"

# Initialize df to store estimates per iteration
all_estimates <- data.frame(matrix(ncol = 5, nrow = 0))
colnames(all_estimates) <- c("Effect", "N", "did", "sc", "sdid")


for(i in 1:length(control_sizes)){
  
  # Grab N and n_treated 
  N <- control_sizes[i]
  
  # Set up list of simulation parameters
  simulation_params <- list(N = control_sizes[i], T = T, n_treated = n_treated, treatment_period = treatment_period,
                           pre_control_trend = pre_control_trend, pre_treated_trend = pre_treated_trend,
                           post_control_trend = post_control_trend, post_treated_trend = post_treated_trend,
                           treatment_effect = treatment_effect, effect = effect)
  
  # Simulation & estimation
  results <- repeated_simulation(simulation_function = treatment_simulation,
                                     simulation_params = simulation_params, iterations = iterations)
  # Grab estimates
  estimates <- results$estimates
  
  # Grab one example df at random index
  df <- results$dfs[[index]]
 
  # Save example df
  write.csv(df, paste0(path, "/Output/Data/Example DFs/example_df_N_", N, "_random.csv"))
  
  # Add additional simulation parameters to estimates
  estimates <- cbind(treatment_effect, N, estimates)
  colnames(estimates) <- c("Effect", "N", "did", "sc", "sdid")
  
  # Append estimates to all_estimates dataframe
  all_estimates <- rbind(all_estimates, estimates)
  
  # Save plot of grouped simulations within each iteration
  plot_grouped_simulations(results$dfs) %>%
    ggsave(filename = paste0(path, "/Output/Plots/data_plot_N_", N, "_random.png"), width = 10, height = 5, units = "in", dpi = 300)
  
  # Print progress info
  print(paste0("Finished simulation for N = ", N, " and n_treated = ", n_treated, " at ", Sys.time()))
}

# Save all estimates
write.csv(all_estimates, paste0(path, "/Output/Data/all_estimates_per_N_random.csv"))
```


#### 1.2 Effect of pre-treatment periods on estimates

To test the influence that the number of pre-treatment periods has on the estimates of
all three methods, all variables except the treatment period, and consequently the 
number of pre-treatment periods, will be kept constant. The number of pre-treatment periods
will be varied from 3 (earliest possible treatment) to 10 (last period). 
In order to still highlight one of SDiD's and SC's main advantages, the overall 
sample size is rather small. Each simulation will again be carried out 1000 times. 

```{r Effect of Treatment periods}
set.seed(100)

# Set addutional simulation parameters
N <- 9

# Setting a lower value than 3 is not possible 
treatment_periods = c(3, 4, 5, 6, 7, 8, 9, 10)

# Initialize df to store estimates per iteration
all_estimates <- data.frame(matrix(ncol = 5, nrow = 0))
colnames(all_estimates) <- c("Effect", "N", "did", "sc", "sdid")

for(i in 1:length(treatment_periods)){
  
  treatment_period <- treatment_periods[i]
  simulation_params <- list(N = N, T = T, n_treated = n_treated, treatment_period = treatment_period,
                           pre_control_trend = pre_control_trend, pre_treated_trend = pre_treated_trend,
                           post_control_trend = post_control_trend, post_treated_trend = post_treated_trend,
                           treatment_effect = treatment_effect, effect = effect)
  
  # Simulation & estimation
  results <- repeated_simulation(simulation_function = treatment_simulation,
                                     simulation_params = simulation_params, iterations = iterations)
  # Grab estimates
  estimates <- results$estimates
  
  # Grab one example df at random index
  df <- results$dfs[[index]]
  
  # Save example df
  write.csv(df, paste0(path, "/Output/Data/Example DFs/example_df_treatment_period_", treatment_period, "_random.csv"))
  
  # Add additional simulation parameters to estimates
  estimates <- cbind(treatment_effect, treatment_period, estimates)
  colnames(estimates) <- c("Effect", "Treatment Period", "did", "sc", "sdid")
  
  # Append estimates to all_estimates dataframe
  all_estimates <- rbind(all_estimates, estimates)

  # Save plot of grouped simulations within each iteration
  plot_grouped_simulations(results$dfs) %>%
    ggsave(filename = paste0(path, "/Output/Plots/data_plot_treatment_period_",
                             treatment_period, "_random.png"), width = 10, height = 5, units = "in", dpi = 300)
  # Print progress info
  print(paste0("Finished simulation for treatment period = ", treatment_period, " at ", Sys.time()))
}

# Save all estimates
write.csv(all_estimates, paste0(path, "/Output/Data/all_estimates_per_period_random.csv"))
```


#### 1.3 Effect of heterogeneity (treatment effect) on estimates

To test the effect that heterogeneous treatment effects have on the three different estimation
methods, the treatment will now be drawn from a Normal distribution with a mean of 
the treatment effect and an increasing standard deviation, which serves as a means to model the
heterogeneity in the treatment effect. The number of treated units will be set to 5%/10% of the
overall population size. However, in order for heterogeneity to "take effect" a sufficient
number of treated units has to be simulated. Slightly larger sample sizes will therefore
be considered in this context. Each simulation will be carried out 1000 times. 

```{r Effect of heterogeneity}
set.seed(100)

# Set up additional parameters
heterogeneity <- c(1, 2, 3, 4, 5)
treatment_period <- T - 2

# Set overall sample size to 100, to allow for 5% and 10% share of treated units
N <- 100
treated_sizes <- c(5, 10)
combinations <- length(heterogeneity) * length(treated_sizes)

# Initialize df to store estimates per iteration
all_estimates <- data.frame(matrix(ncol = 6, nrow = 0))
colnames(all_estimates) <- c("Effect", "Heterogeneity", "treated", "did", "sc", "sdid")

# Loop over combinations of heterogeneity and treated sizes
for(i in 1:length(treated_sizes)){
  
  n_treated <- treated_sizes[i]
  
    for (j in 1:length(heterogeneity)){
      
      deviation <- heterogeneity[j]
    
      simulation_params <- list(N = N, T = T, n_treated = n_treated, treatment_period = treatment_period,
                           pre_control_trend = pre_control_trend, pre_treated_trend = pre_treated_trend,
                           post_control_trend = post_control_trend, post_treated_trend = post_treated_trend,
                           treatment_effect = treatment_effect, deviation = deviation, effect = effect)
  
      # Simulation & estimation
      results <- repeated_simulation(simulation_function = heterogeneous_treatment_simulation,
                                     simulation_params = simulation_params, iterations = iterations)
      # Grab estimates
      estimates <- results$estimates
  
      # Grab one example df at random index
      df <- results$dfs[[index]]
  
      # Save example df
      write.csv(df, paste0(path, "/Output/Data/Example DFs/example_df_deviation", deviation, "_random.csv"))
      
      # Add additional simulation parameters to estimates
      estimates <- cbind(treatment_effect, deviation, n_treated, estimates)
      colnames(estimates) <- c("Effect", "Heterogeneity", "Treated", "did", "sc", "sdid")
      
      # Append estimates to all_estimates dataframe
      all_estimates <- rbind(all_estimates, estimates)

      # Save plot of grouped simulations within each iteration
      plot_grouped_simulations(results$dfs) %>%
      ggsave(filename = paste0(path, "/Output/Plots/data_plot_dev_",
                             deviation, "_n_treated_", n_treated, "_random.png"), width = 10, height = 5, units = "in", dpi = 300)

      # Print progress info
      print(paste0("Finished simulation for deviation = ", deviation, " and n_treated = ", n_treated, " at ", Sys.time()))
  }
}

# Save all estimates
write.csv(all_estimates, paste0(path, "/Output/Data/all_estimates_per_deviation_random.csv"))
```


### 1.4 Violation of the parallel trends assumption

The assumption of parallel trends is crucial for identifying the treatment effect
in the context of DiD. In order to test how well the three different methods can
cope with violations of this assumption, the post-treatment trends will be set to 
sightly differ between the two groups. Pre-treatment trends are still parallel.
Setting the overall sample size to be sufficiently large in order to return reliable estimates,
different degrees of violation will be considered. Each simulation will be carried out 1000 times. 

```{r Violation of parallel trends}
set.seed(100)

# Set additional parameters
N <- 100
n_treated <- 5
post_treated_trends <- c(0.2, 0.3, 0.5, 1)

# Initialize df to store estimates per iteration
all_estimates <- data.frame(matrix(ncol = 5, nrow = 0))
colnames(all_estimates) <- c("Effect", "Post Treated Trend", "did", "sc", "sdid")

for(i in 1:length(post_treated_trends)){
  
  post_treated_trend <- post_treated_trends[i]
  
  simulation_params <- list(N = N, T = T, n_treated = n_treated, treatment_period = treatment_period,
                           pre_control_trend = pre_control_trend, pre_treated_trend = pre_treated_trend,
                           post_control_trend = post_control_trend, post_treated_trend = post_treated_trend,
                           treatment_effect = treatment_effect, effect = effect)
  
  # Simulation & estimation
  results <- repeated_simulation(simulation_function = treatment_simulation,
                                     simulation_params = simulation_params, iterations = iterations)
  # Grab estimates
  estimates <- results$estimates
  
  # Grab one example df at random index
  df <- results$dfs[[index]]
  
  # Save example df
  write.csv(df, paste0(path, "/Output/Data/Example DFs/example_df_post_treated_trend_", post_treated_trend, "_random.csv"))
  
  # Add additional simulation parameters to estimates
  estimates <- cbind(treatment_effect, post_treated_trend, estimates)
  colnames(estimates) <- c("Effect", "Post Treated Trend", "did", "sc", "sdid")
  
  # Append estimates to all_estimates dataframe
  all_estimates <- rbind(all_estimates, estimates)
  
  # Save plot of grouped simulations within each iteration
  plot_grouped_simulations(results$dfs) %>%
    ggsave(filename = paste0(path, "/Output/Plots/data_plot_post_treated_trend_",
                             post_treated_trend, "_random.png"), width = 10, height = 5, units = "in", dpi = 300)
  
  # Print progress info
  print(paste0("Finished simulation for post treated trend = ", post_treated_trend, " at ", Sys.time()))
}

# Save all estimates
write.csv(all_estimates, paste0(path, "/Output/Data/all_estimates_per_post_treated_trend_random.csv"))
```


### 1.5 Assessing the computation time per method 

Since SDiD and SC are computationally more demanding than DiD, comparing their differences
in terms of computation time is an important aspect, when assessing their overall
performance. In order to contrast the computation times, the simpler setting of 
homogeneous treatment will be regarded. 7 different sample sizes will be considered 
and the number of treated units always amounts to 10% of the overall population size.
In each iteration, the three different estimation methods are carried out separately and
the computation time will be tracked. Each simulation (sample size) will be carried out 1000 times. 

```{r Contrasting computation times}
set.seed(100)

# Set parameters for simulation
population_sizes <- c(10, 50, 100, 250, 500, 1000, 5000)
post_treated_trend <- 0.1

# Construct df to store mean computation times
all_computation_times <- data.frame(matrix(ncol = 4, nrow = 0))
colnames(all_computation_times) <- c("N", "SDiD", "SD", "TWFE")

# Set up list of simulation parameters

for (i in 1:length(population_sizes)){
 
  # Set N and n_treated 
  N <- 0.9 * population_sizes[i]
  n_treated <- 0.1 * population_sizes[i]
  
  # Collect parameters
  simulation_params <- list(N = N, T = T, n_treated = n_treated, treatment_period = treatment_period,
                           pre_control_trend = pre_control_trend, pre_treated_trend = pre_treated_trend,
                           post_control_trend = post_control_trend, post_treated_trend = post_treated_trend,
                           treatment_effect = treatment_effect)
  # Conduct simulation
  times <- contrast_simulation(simulation_function = treatment_simulation,
                               simulation_params = simulation_params, iterations = iterations)
  
  # Append to all_computation_times
  all_computation_times <- rbind(all_computation_times, times)

  # Print progress info
  print(paste0("Finished simulation for N = ", N, " and n_treated = ", n_treated, " at ", Sys.time()))
}

# Save results for later use
write.csv(all_computation_times, paste0(path, "/Output/Data/computation_times_per_N_random.csv"))
```

